---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

```{r setup}
library(tidyverse)
library(here)
library(skimr)
library(infer)
```

```{r import data}
cows <- readr::read_csv(here::here("projects/project_4/data/swiss_cows_data.csv"))
```
#Part 2
Perform a t-test using the first 3 cows of each breed and answer the question:
Are Brown Swiss cows heavier than Swiss Red Holstein cows ?

```{r}
cows_03 <- cows |> 
  filter(num <= 3)
```

```{r summary table}
cows_03 |> 
  group_by(breed) |> 
  skim() |> 
  print()
```
The t-test provides you with an objective tool to compare the two obtained means.
```{r t-test}
my_test <- cows_03 %>% t_test(formula = weight ~ breed,
                              order = c("Brown_Swiss", "Swiss_Red_Holstein"),
                              conf_level = 0.95)

print(my_test)
```
You can visualize the steps of the t-test process with the following code:
```{r}
t_obs <- my_test %>%
  select(statistic)

cows_03 %>%
  specify(formula = weight ~ breed) %>%
  hypothesize(null = 'independence') %>%
  calculate(stat = "t") %>%
  visualise(method = "theoretical") +
  shade_p_value(obs_stat = t_obs, direction = "both") +
  theme_minimal() +
  labs(caption = " The area of the red region under the density curve
       corresponds actually to the p-value obtained in my_test.")
```

##Part 3
Perform a t-test using only the first cow of each breed

```{r}
cows_01 <- cows |> 
  filter(num == 1) 

my_test_01 <- cows_03 %>% t_test(formula = weight ~ breed,
                              order = c("Brown_Swiss", "Swiss_Red_Holstein"),
                              conf_level = 0.95)

print(my_test_01)

```
## Part 4
Perform a t-test using all the cows of each breed
```{r}

cows |> 
  group_by(breed) |> 
  skim() |> 
  print()

my_test <- cows %>% t_test(formula = weight ~ breed,
                              order = c("Brown_Swiss", "Swiss_Red_Holstein"),
                              conf_level = 0.95)

print(my_test)

t_obs <- my_test %>%
  select(statistic)

cows %>%
  specify(formula = weight ~ breed) %>%
  hypothesize(null = 'independence') %>%
  calculate(stat = "t") %>%
  visualise(method = "theoretical") +
  shade_p_value(obs_stat = t_obs, direction = "both") +
  theme_minimal() +
  labs(caption = "This confidence interval does not contain the zero value. 
       The cows data set provides therefore enough evidence that Brown Swiss are heavier than Swiss Red Holstein.")
  
```
The difference in weight between the two breeds of cows, based on the p-value of `r my_test$p_value` is statistically significant.

As the p-value is smaller than 0.05 and equals to `r my_test$p_value`, we can reject the null hypothesis that there is no difference in the weight, between two cow breeds `r unique(cows$breed)`. In other words, we do  have enough evidence to state that there is a difference.

##Part 5
```{r import fitness data}
fitness_members <- read_csv(here("projects/project_4/data/fitness_members.csv")) |> 
  as_tibble()
fitness_tracking <- read_csv(here("projects/project_4/data/fitness_tracking.csv")) |> 
  as_tibble()
```

##Part 6
After some data handling, perform a t-test to answer the question:
Do we observe a different evolution of BMI from week 0 to week 12 in the different fitness club membership categories ?
 
```{r transform data}
tracking_long <- fitness_tracking |> 
  pivot_longer(cols = !id, names_to = "weeks", values_drop_na = TRUE) 

members_weight <- fitness_members |> 
  select(id,weight, height, m_category) |> 
  mutate(weeks = "wk_000") 

tracking_full <- tracking_long |> 
  rename(weight = value) |> 
  bind_rows(members_weight) |> 
  arrange(id, weeks) |> 
  fill(height, m_category) |> 
  mutate(bmi = weight/(height/100)^2)

```

Case use:
- When you have a numerical variable and two groups and you want to
test if the average of this numerical variable is different in the two
groups

Conditions:

- the data comes from two independent groups

- the data from the two groups needs to be normally distributed

- the variance of both groups needs to be approximately equal


```{r plot the distribiution}

tracking_full |> 
  ggplot(aes(x = bmi)) +
  geom_histogram() +
  facet_wrap(vars(m_category))

```

```{r t_test}

tracking_t_test <- tracking_full |> 
  filter(m_category == "Economy" | m_category == "Balance")

tracking_t_test |> 
  group_by(m_category) |> 
  skim() |> 
  print()

test_E_B <- tracking_t_test |> 
  t_test(formula = bmi ~ m_category,
         order = c("Economy", "Balance"),
         conf_level = 0.95) |> 
  print()

t_obs_E_B <- test_E_B %>%
  select(statistic)

tracking_t_test %>%
  specify(formula = bmi ~ m_category) %>%
  hypothesize(null = 'independence') %>%
  calculate(stat = "t") %>%
  visualise(method = "theoretical") +
  shade_p_value(obs_stat = t_obs_E_B, direction = "both") +
  theme_minimal() +
  labs(caption = "This confidence interval does not contain the zero value. 
       The cows data set provides therefore enough evidence that Brown Swiss are heavier than Swiss Red Holstein.")
```

##Part 7
When we compare the number of members in the Premium category to the other categories Economic and Balance, do we observe a similar pattern for female and male fitness members ?

```{r}
fitness_members <-  fitness_members %>%
  mutate(m_category = factor(m_category, levels = c("Economy", "Balance", "Premium")))

chisq_value <- fitness_members %>%
chisq_test(m_category ~ gender)

fitness_members %>%
  specify(formula = m_category ~ gender) %>%
  hypothesize(null = 'independence') %>%
  calculate(stat = "t") %>%
  visualise(method = "theoretical") +
  shade_p_value(obs_stat = chisq_value, direction = "both") +
  theme_minimal() +
  labs(caption = "This confidence interval does not contain the zero value. 
       The cows data set provides therefore enough evidence that Brown Swiss are heavier than Swiss Red Holstein.")
```

