---
title: "Fitness Club"
output: html_notebook
---

```{r setup}
library(tidyverse)
library(here)
```

```{r get data}
members <- read_csv(here("projects/project_3/data/fitness_members.csv")) |> 
  as_tibble()
tracking <- read_csv(here("projects/project_3/data/fitness_tracking.csv")) |> 
  as_tibble()
  
```

##Fitness Club Report

The owners of a Fitness Club would like to get an overview of their club members, and perform some analyses of the data they collect on a regular basis.
"Who are our members ?"


##Q.1 
A simple R function from the {janitor} package could be used to answer the question "What is the proportion of female and male Fitness Club members ?". Do you remember this function ? With this function, we get the following output in R:

```{r}
fitness_members %>% tabyl(gender) %>% adorn_pct_formatting(digits = 1)
```
##Q.2
How many successful recommendations were made by each member ?
```{r recommendations}
recommendations <- members |> 
  filter(recommendation_from != "NA") |> 
  count(is.na(recommendation_from))

recommendations
```

```{r single member}
members |> 
   count(recommendation_from) |> 
  filter(recommendation_from == "000115") 
```

```{r max recommendation}
members |> 
  count(recommendation_from) |> 
  filter(recommendation_from != "NA") |> 
  summarise(max = max(n))
```

```{r highest member}
members |> 
  count(recommendation_from) |> 
  filter(recommendation_from != "NA") |> 
  arrange(desc(n))
```


How many female members in the Premium membership category made one or more successful recommendations ?
```{r}
recommenders <- members |> 
  filter(gender =="F", m_category == "Premium", recommendation_from != "NA") |> 
  distinct(recommendation_from)

ids <- as_factor(recommenders$recommendation_from)

members |> 
  filter(id == ids)
```

```{r BMI index}

members |> 
  mutate(bmi = weight/(height/100)^2) |> 
  filter(id == "000042") |> 
  View()


```

```{r tranform tracking}
tracking_long <- tracking |> 
  pivot_longer(cols = !id, names_to = "weeks", values_drop_na = TRUE) 

members_weight <- members |> 
  select(id,weight) |> 
  mutate(weeks = "wk_000") 

tracking_full <- tracking_long |> 
  rename(weight = value) |> 
  bind_rows(members_weight) |> 
  arrange(id, weeks) 

```


```{r}
members_ids <- members$id
tracking_ids <- tracking$id

members |> 
  filter(id != tracking_ids) 

```
```{r}
tracking |> 
  filter(id %in% c("000417", "000418","000419", "000420"))
```
Use the data set fitness_tracking_long to compute weekly BMI values for each member. Again, a very useful function from the tidyverse package can help you here.

What is the BMI value of member 000024 at week 11 ?
```{r Part9}

members |> 
  select(-weight) |> 
  right_join(tracking_full, by = "id") |> 
  mutate(bmi = weight/(height/100)^2) |> 
  filter(id == "000024", weeks == "wk_011") |> 
  View()

```

```{r Part10}
members |> 
  select(-weight) |> 
  right_join(tracking_full, by = "id") |> 
  mutate(bmi = weight/(height/100)^2) |> 
  mutate(bmi_change = weight/lag(weight)-1) |> 
  filter(id == "000015")
```

